Coherent Hyper-Raman Four Wave Mixing Vibrational Spectroscopy

### 2024-07-22 paper.tex
whoops

\section{Mixed-Domain HDFG}\label{mixeddomain}
The properties of steady state HDFG (complete pulse overlap) are useful for understanding the selection rules that drive HDFG output, motivating time domain experiments.
Time domain HDFG could be a useful alternative technique for measuring single quantum coherence dephasing times.
Working under the rotating wave approximation and neglecting spatial components, the output polarization is written in the time domain as 
\begin{equation}
	\begin{split}
			\vec{P}(t) &= \int_0^\infty \mathrm{d}t_3 \int_0^\infty \mathrm{d}t_2 \int_0^\infty \mathrm{d}t_1 R^{(3)}(t_1, t_2, t_3)  \vdots \vec{E}_3(t-t_3) \\
			&\vec{E}_2(t-t_3-t_2 - \tau_{23}) \vec{E}_1(t-t_3-t_2-t_1 - \tau_{13}) 
	\end{split}
\end{equation}
where the electric fields are labeled according to their placement in the WMEL diagrams, $\tau_{ij} = \tau_i - \tau_j$ is the time delay between pulses $i$ and $j$, and R is the response function. \cite{RN287} 
Here, we will focus on the response function formalism for singly resonant HDFG, as the extension to doubly resonant HDFG has been treated by Cho. \cite{Cho2001}
The response function for the HDFG pathway illustrated in \autoref{fig:hdfg}a, assuming $\omega_2$ and $\omega_3$ are temporally overlapped, not electronically resonant, and $\rho(-\infty) = 1$, in the limit of homogeneous broadening is \cite{Cho2001, Meyer2004, RN367}
\begin{equation}
	R^{(3)}(t_1) = \frac{i}{\hbar} \beta_{ijk}(t_1) \mu_l(0) \exp(-i\Delta_{gv}t_1) \theta(t_1) 
\end{equation}  
where $\theta$ is the Heaviside function.
The pure time-domain HDFG output reports on the dephasing characteristics of the $\ket{g}\bra{v}$ coherence. 
This method provides practitioners of sum frequency generation the ability to probe isotropic dephasing dynamics without many meaningful changes in their optical setup, and thus compare $\ket{g}\bra{v}$ dephasing in the bulk and at the interface.\cite{RN224}

>>>>

\section{Mixed-Domain HDFG}\label{mixeddomain}
The properties of steady state HDFG (complete pulse overlap) are useful for understanding the selection rules that drive HDFG output, motivating time domain experiments.
Time domain HDFG could be a useful alternative technique for measuring single quantum coherence dephasing times.
Working under the rotating wave approximation and neglecting spatial components, the output polarization is written in the time domain as 
\begin{equation}
	\begin{split}
			\vec{P}(t) &= \int_0^\infty \mathrm{d}t_3 \int_0^\infty \mathrm{d}t_2 \int_0^\infty \mathrm{d}t_1 R^{(3)}(t_1, t_2, t_3)  \vdots \vec{E}_3(t-t_3) \\
			&\vec{E}_2(t-t_3-t_2 - \tau_{23}) \vec{E}_1(t-t_3-t_2-t_1 - \tau_{13}) 
	\end{split}
\end{equation}
where the electric fields are labeled according to their placement in the WMEL diagrams, $\tau_{ij} = \tau_i - \tau_j$ is the time delay between pulses $i$ and $j$, and R is the response function. \cite{RN287} 
Here, we will focus on the response function formalism for singly resonant HDFG, as the extension to doubly resonant HSFG, easily transferable to DR-HDFG, has been treated by Cho. \cite{Cho2001}
The response function for the HDFG pathway illustrated in \autoref{fig:hdfg}a, assuming $\omega_2$ and $\omega_3$ are temporally overlapped, not electronically resonant, and $\rho(-\infty) = 1$, in the limit of homogeneous broadening is \cite{Cho2001, Meyer2004, RN367}
\begin{equation}
	R^{(3)}(t_1) = \frac{i}{\hbar} \beta_{ijk}(t_1) \mu_l(0) \exp(-i\Delta_{gv}t_1) \theta(t_1) 
\end{equation}  
where $\theta$ is the Heaviside function.
The pure time-domain HDFG output reports on the dephasing characteristics of the $\ket{g}\bra{v}$ coherence. 
This method provides practitioners of sum frequency generation the ability to probe isotropic dephasing dynamics without many meaningful changes in their optical setup, and thus compare $\ket{g}\bra{v}$ dephasing in the bulk and at the interface.\cite{RN224}
